---
title: "scRNA-cc"
output:
  html_document: default
---
## Series GSE134691



```{r cars, message=TRUE, warning=TRUE}
# if (!requireNamespace("BiocManager", quietly = TRUE))
#   install.packages("BiocManager")
# library(BiocManager)
# # BiocManager::install("GEOquery")
# library(GEOquery)
# library(Seurat)  
# library(dplyr)
# library(patchwork)
# if (!requireNamespace("BiocManager", quietly = TRUE))
#   +   install.packages("BiocManager")
#  
#   BiocManager::install("fgsea")
  # 
  # library(Seurat)  
  # 
  # #install_github('immunogenomics/presto')
  # library(presto)  

new_counts <- read.table(file="./GSM3946326_SIA_5_Seurat_count_matrix.txt",row.names = 1)
head(new_counts)
```

## Including Plots


```{r pressure, echo=FALSE}
pbmc.data <- new_counts
at_least_one <- apply(pbmc.data, 2, function(x) sum(x>0))
hist(at_least_one, breaks = 100,
     main = "Distribution of detected genes",
     xlab = "Genes with at least one tag")
```



```{r}
mydata <- CreateSeuratObject(counts = new_counts, min.cells = 3, project = "mydata_scRNAseq")
mydata
```

##Initialize Seurat object with pbmc data

```{r message=TRUE, warning=TRUE}
pbmc <- mydata
head(pbmc$RNA@data[,1:5])
```

```{r}
pbmc[["percent.mt"]] <- PercentageFeatureSet(pbmc, pattern = "^mt-")
head(pbmc@meta.data, 5)
```

```{r}
#Draw a picture to view the number of genes, the number of UMI, and the proportion of mitochondrial genes
VlnPlot(pbmc, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)

plot1 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
plot1 + plot2
```

# Quality control
#
# Screen for cells with more than 2500 or less than 200 genes detected
# The number of mitochondrial genes in a single cell exceeds >5%

```{r}
pbmc <- subset(pbmc, subset = nFeature_RNA > 200 & nFeature_RNA < 2500 & percent.mt < 5)
hist(colSums(pbmc$RNA@data),
     breaks = 100,
     main = "Total expression before normalisation",
     xlab = "Sum of expression")
```

## Data Standardization

#The default data standardization method is LogNormalize, the total expression of each cell is standardized to 10000, and then log takes the logarithm; the result is stored in pbmc[["RNA"]]@data.
#Before standardization, the total expression of each cell
 
```{r}
hist(colSums(pbmc$RNA@data),
     breaks = 100,
     main = "Total expression before normalisation",
     xlab = "Sum of expression")
```
```{r}
pbmc <- NormalizeData(pbmc, normalization.method = "LogNormalize", scale.factor = 10000)
```


#After normalization, the total expression of each cell

```{r}
hist(colSums(pbmc$RNA@data),
     breaks = 100,
     main = "Total expression after normalisation",
     xlab = "Sum of expression")  
```
 

##  Change gene identification

#To identify genes with highly variable expression between cells, 
#follow-up studies need to focus on these genes.
#Seurat's built-in FindVariableFeatures() function first calculates the mean and variance
#of each gene, and directly simulates the relationship. 2000 genes are returned by default.

```{r}
pbmc <- FindVariableFeatures(pbmc, selection.method = "vst", nfeatures = 2000)

```
# 10 genes with the most dramatic changes in expression
 
```{r}
top10 <- head(VariableFeatures(pbmc), 10) 
head(pbmc$RNA@var.features,10)
plot1 <- VariableFeaturePlot(pbmc)

```
 # # Draw the genes whose expression changes to observe their distribution
```{r}
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1
plot2
```
 
##  Data scaling
```{r}

all.genes <- rownames(pbmc)
pbmc <- ScaleData(pbmc, features = all.genes)
pbmc <- ScaleData(pbmc, vars.to.regress = "percent.mt")

```

```{r}
pbmc <- RunPCA(pbmc, features = VariableFeatures(object = pbmc))
```


```{r}
pbmcTsne <- RunTSNE(pbmc,dims.use=1:10,do.fast=TRUE)
```


```{r}
TSNEPlot(pbmcTsne)
```
 
 
 
 ##View the gene set that has a greater impact on each principal component

```{r}
print(pbmc[["pca"]], dims = 1:5, nfeatures = 5)
```

#Visualization of gene sets that have a greater impact on each principal component
 
```{r}

VizDimLoadings(pbmc, dims = 1:2, reduction = "pca")


```

```{r}
DimPlot(pbmc, reduction = "pca",split.by = 'ident')
```
```{r}
DimHeatmap(pbmc, dims = 1, cells = 500, balanced = TRUE)
```

```{r}
DimHeatmap(pbmc, dims = 1:15, cells = 500, balanced = TRUE)
```
```{r}
pbmc <- JackStraw(pbmc, num.replicate = 100)
```

```{r}

pbmc <- ScoreJackStraw(pbmc, dims = 1:20)
JackStrawPlot(pbmc, dims = 1:15)

```

```{r}
ElbowPlot(pbmc)
```

```{r}
pbmc <- FindNeighbors(pbmc, dims = 1:10)
pbmc <- FindClusters(pbmc, resolution = 0.5)
```
#Check which group the cell belongs to


```{r}
head(Idents(pbmc), 5)
```


```{r}

# install UMAP： reticulate::py_install(packages ='umap-learn')
pbmc <- RunUMAP(pbmc, dims = 1:10)
DimPlot(pbmc, reduction = "umap")
```

#Add tags for cell group xiba


```{r}
DimPlot(pbmc, reduction = "umap",label = TRUE)
LabelClusters(DimPlot(pbmc, reduction = "umap"),id = 'ident')
```


```{r}
saveRDS(pbmc, file = "./pbmc.rds")
```

#######################   KEGG   ################################
# Looking for differentially expressed genes (cluster biomarkers)
# find all markers of cluster 1
```{r}
cluster1.markers <- FindMarkers(pbmc, ident.1 = 1, min.pct = 0.25)
head(cluster1.markers, n = 5)
```
# find markers for every cluster compared to all remaining cells, report only the positive ones
```{r message=TRUE, warning=TRUE}
pbmc.markers <- FindAllMarkers(pbmc, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
```


```{r}
saveRDS(pbmc, "./pbmc_day5.rds")
```

#For GSEA, all genetic information is required
```{r message=TRUE, warning=TRUE}
pbmc<- readRDS("./pbmc_day5.rds")
# library(devtools)
# library(RPresto)
# library(Rcpp)
```

 
# In order to perform gene set enrichment analysis, the gene set needs to be annotated first.  
# Use fgsea for gene set enrichment
```{r}
# dplyr::count(pbmc.genes, group)
# install.packages("msigdbr")
# library(msigdbr)
# library(fgsea)
# library(ggplot2)

```

#See what species 
```{r}
msigdbr_show_species()
```


```{r}
m_df<- msigdbr(species = "Mus musculus", category = "C7") 
head(m_df)
```


 
 
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
